Low-Thrust Trajectory Design Near Asteroids Using Reachability Sets

### 2016-08-04 manuscript.tex
Starting on equations of motion

 \title{Low-Thrust Trajectory Design Near Asteroids Using Invariant Manifolds and Reachability Sets}

@@

Cite Scheeres orbits close to 4769 Castalia
\subsection{Polyhedron Gravity Model}

@@

\subsection{Spacecraft Equations of Motion}
Cite scheeres and his book

@@

Periodic orbits

\section{Reachability Set}

@@

Show \Poincare section

Optimal control problem

@@

Show partial derivatives

@@

>>>>

 \title{Low-Thrust Trajectory Design Near Asteroids Using Reachability Sets}

@@

Cite Scheeres orbits close to 4769 Castalia

Assuming constant rotation rate for asteroid

\subsection{Polyhedron Gravity Model}

@@

\subsection{Spacecraft Equations of Motion}

The motion of a massless particle, or spacecraft, about an asteroid shares many similarities with that of the three-body problem.
As is typical in the three-body problem, the equations of motion are usually represented in a uniformly rotating frame aligned with the two primaries.
Similarily, the equations of motion about an asteroid are also defined in a body-fixed frame with uniform rotation.
In this reference frame, the gravitational potential field is time invariant and only a function of the position of the particle.
In addition, since the rotational rate of the asteroid is constant the equations of motion are time invariant.
Finally, the use of the rotating reference frame allows for much greater insight into the dynamic structure of the behavior around the asteroid.

We define a reference frame originating at the center of mass of the asteroid.

Cite scheeres and his book

@@

\subsection{Determining Periodic Orbits}

Periodic orbit computation summary. Cite Scheeres 2000 (Evaluation of the Dynamic environment of an asteroid)

\section{Reachability Set on \Poincare Section}
Define reachability set

Define \Poincare section

@@

Formulate OCP to generate the reachability set

@@

@@

Thruster magnitude is chosen to emulate some real thrusters - cite the Dawn paper
